%-------------------------
% Resume in Latex
% Author : Nutthawat Panyangnoi
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}

    }

    \newcommand{\resumeProjectHeading}[2]{
      \item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \textbf{\small #2}\\
      \end{tabular*}\vspace{-7pt}
  }

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\vspace{-10pt}
\begin{center}
    {\Huge \scshape Nutthawat Panyangnoi}\\ 
    \vspace{1pt}{https://kur0neko.com}\\ \vspace{1pt} 
    \vspace{0.5pt} San Jose, CA 95112 \\ \vspace{0.5pt}
    \small \raisebox{-0.1\height}\faPhone\ (209) 407-9730 ~ \href{mailto:panyangnoi.nutthawat@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{panyangnoi.nutthawat@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/nathan-panyangnoi/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/nathan-panyangnoi/}}  ~
    \href{https://github.com/kur0neko}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/kur0neko}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jose State University}{Aug 2022 -- May 2025}
      {Bachelor of Science in Computer Engineering, Minor in Computer Science}{San Jose, CA}
      \resumeSubheading
      {Las Positas College}{Aug 2018 -- May 2022}
      {Associate of Science in Computer Science, Minor in Math}{Livermore, CA}
      \resumeSubheading
      {King Mongkut’s University of Technology Thonburi}{May 2010 -- June 2012}
      {Bachelor of Science in Computer Science} {Did not complete the degree due to family relocation to U.S.}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[left=0.15in, label={}]
    \small{
    \item \textbf{Programing skills:} Python, CSS, HTML, mySQL, C/C++,Java, Javascript, MongoDB, NodeJS, PHP, HDL (Verilog/ SystemVerilog) \\
    \textbf{Tools \& Frameworks:} Git / GitHub, GDB (Debuggers), SPICE (LtSpice), Flask, Numpy, Pandas, Pytorch, AutoCAD, Adobe Creative Suit, Microsoft Office, VMware, Docker  \\
    \textbf{Shell Scripting:} BASH Script, Window Power Shell \\
    \textbf{Networking \& Protocols:} TCP/IP, DNS/DHCP, NAS, VPN Configuration \\
    \textbf{Hardware \& Electrical:} Schematics,testing devices (Oscilloscopes, Multimeters, Frequency generators), soldering \\
    \textbf{Systems \& Software:} Windows, Linux \\
    }
\end{itemize}
\vspace{-15pt}

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-1pt, parsep=3pt]
                \item \small Software Engineering
                \item \small Digital Circuit Design 
                \item \small Advanced data structures and algorithms
                \item \small Embedded Systems
                \item \small SQL 
                \item \small Computer Networks
                \item \small Microprocessors Design
                \item \small Computer Architecture
                \item \small Machine Learning
                \item \small OS Design
                \item \small Assembly Language (MIPS, NASM, MASM)
            \end{itemize}
        \end{multicols}
        \vspace*{1.5\multicolsep}
    %\resumeSubHeadingListEnd
\vspace{8pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

   \resumeSubheading
    {NASA (NASA L'SPACE Proposal Writing Academy)}{August 2024 - Present}
    {Researcher}{remote}
    \resumeItemListStart
        \resumeItem{Collaborating with multi-disciplinary teams to research and develop the innovative solutions proposal to NASA's pain points.}
        \resumeItem{Apply trade Study TRL to identify the right choice of innovative solution.}
      \resumeItemListEnd

    \resumeSubheading
      {NASA (NASA L'SPACE Mission Concept Academy)}{April 2024 -- August 2024}
      {Program Analyst \& Computer Hardware Engineer }{remote}
      \resumeItemListStart
        \resumeItem{Conducted cost estimation for simulated lunar missions, using advanced methodologies and tools such as NASA MCCET and NICM CERs/SERs. }
        \resumeItem{Managed mission schedules from prelaunch to closeout, collaborating with project managers, scientists, and engineers. }
        \resumeItem{Engineered the design of the Command and Data Handling (CDH) subsystem, contributing to mission critical components of the project.}
      \resumeItemListEnd

    \resumeSubheading
      {Mountain Cascade, Inc}{March 2020 - August 2023}
      {IT technician \& IT manager}{Livermore, CA}
      \resumeItemListStart
        \resumeItem{Offers customer service and satisfaction for engineers, project managers and field workers.}
        \resumeItem{Optimized Window Virtual Machine Servers, enabling seamless remote engineering work.}
        \resumeItem{Diagnosed and resolved complex hardware and software issues, with a specialization in Windows environments.}
        \resumeItem{Enforced security policies and systems on Windows servers to ensure data integrity and protection, including technology upgrades and server optimization, aligning with organizational objectives.}
        \resumeItem{Provided comprehensive IT support, including HCSS, Sage products, and Timberline Accounting. }
      \resumeItemListEnd

    \newpage

    \resumeSubheading
      {Amber System Technology}{April 2018 - March 2020 }
      {Frontend Software Engineer}{Pleasanton, CA}
      \resumeItemListStart
        \resumeItem{Create intuitive UX/UI designs for POS systems to improve user experience and customer engagement.}
        \resumeItem{Oversee web content and development projects, ensuring consistency with branding aligned to client requirements.}
        \resumeItem{Give technical cumstomers support via Cisco VoIP, for efficient and effective problem resolution.}
      \resumeItemListEnd

    \resumeSubheading
      {Volcano Splash Drinks (Small Private Family business)}{August 2013 - December 2018}
      {Barista and Operations Lead}{Tracy, CA}
      \resumeItemListStart
        \resumeItem{Optimized business layout and processes, significantly enhancing customer flow and operational efficiency}
        \resumeItem{implement solution operating procedures, ensuring consistent delivery of top-quality customer service}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Neural Network Machine Learning} \\ \emph{Python, Pytorch, Pandas, Numpy}}{2024}
    \resumeItemListStart
        \resumeItem{Implement Neural Network that can predict the number from the user prompt.}
       \resumeItemListEnd

       \resumeProjectHeading
       {\textbf{Note Hub} \\ \emph{Python, Flask, SQLAlchemy, Jinja2, EmailValidator, anaconda}}{2023}
       \resumeItemListStart
           \resumeItem{NoteHub is the Note Web application built with Flask python framework, WTforms, SQL alchemy, and Jinja web template engine.}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Encryption Decryption program} \\ \emph{NASMx86}}{2021}
          \resumeItemListStart
              \resumeItem{Implementing Assembly programing x86 64bits Encryption and Decryption File.}
             \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{CUBE3 Satellite Club}{Aug 2024 -- Present}{Controls (Programmer Active Member)}{}
            \resumeItemListStart
                \resumeItem{Collaborate with group of engineering developing software to control the Satellite}
        \resumeItemListEnd

        \resumeSubheading{SJSU Competitive programing }{Aug 2024 -- Present}{Regular Active member}{}
        \resumeItemListStart
            \resumeItem{Regularly solve challenges on platforms like LeetCode to improve coding proficiency and prepare for programming competitions.}
            \resumeItem{Participate in competitive programming contests to apply skills in real-time scenarios and improve problem-solving speed and accuracy.}
            \resumeItem{Relearn and enhance understanding of data structures and algorithms through hands-on practice and problem-solving.}
       \resumeItemListEnd

       \resumeSubheading{SJSU machine learning}{Aug 2023 -- Present}{Regular Active member}{}
            \resumeItemListStart
                \resumeItem{Participate in collaborative research and implementation of various machine learning projects, contributing to the development and refinement of models, algorithms, and applications.}
        \resumeItemListEnd

        \resumeSubheading{Tau Beta Pi Engineering Honor Society}{January 2023 -- Present}{Regular Active member}{}
            \resumeItemListStart
                \resumeItem{Selected for membership in recognition of academic excellence and leadership potential in the field of engineering.}
                \resumeItem{Participate in club meetings, events, and activities aimed at promoting professional development, community service, and academic collaboration.}
                \resumeItem{Engage in networking opportunities with distinguished professionals, alumni, and fellow members to enhance career prospects and technical knowledge.}
                
        \resumeItemListEnd
        
        \newpage
        \resumeSubheading{SJSU Software Engineering club}{Aug 2022 -- Present}{Regular Active member}{}
            \resumeItemListStart
                \resumeItem{Contribute to discussions on software engineering best practices, coding standards, and technologies}
        \resumeItemListEnd

        \resumeSubheading{MESA Engineering SJSU}{Aug 2022 -- Present}{Regular Active member}{}
            \resumeItemListStart
                \resumeItem{Participate in academic enrichment programs, workshops, and events aimed at supporting underrepresented students in engineering, mathematics, and science.}
                \resumeItem{Collaborate with fellow students in projects, study groups, and hands-on activities designed to enhance technical skills and knowledge in engineering disciplines.}
                \resumeItem{Engage in leadership and professional development opportunities provided by MESA, such as networking events, career panels, and mentorship programs.}
        \resumeItemListEnd
        \resumeSubHeadingListEnd
   

    \vspace{-16pt}
%-----------AWARDS-----------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Awards:}{}{}{}
        \vspace{-8pt} % Adjust spacing if needed
        San Jose State University Fall 2022 Dean’s List Awards
        Las Positas College Fall 2021 Dean’s List Awards  
    \vspace{5pt}
    \resumeSubheading
        {Scholarship:}{}{}{}
        \vspace{5pt} % Adjust spacing if needed
        Las Positas College EOPS's Scholarship 2020-2022
  \resumeSubHeadingListEnd
\end{document}
